A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-28 paper.tex
Work in progress
Still working.

@@

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
    \begin{tabular}{lll}
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\
    Population & 60 & 60 \\
    Max Generation & 20 & 20 \\
    Stagnation & Off & 10 \\
    Chromosome Length & 20 & 20 \\
    Target Fitness & 20 & 20 \\
    Crossover Rate & 100 & 100 \\
    Mutation Rate & 7 & 7 \\
    Tournament Rate & 100 & 50 \\
    Tournament Sample & 3 & 4 \\
    Open Reproduction Rate & NA & 5 \\
    Closed Reproduction Rate & NA & 45 \\
    Max Age & NA & 80 \\
    Base Approval & NA & 80 \\
    Goal Approval & NA & 100
    \end{tabular}
    \end{table}

>>>>

\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{22C5}{-}

@@

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab1}
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
    Population & 60 & 60 \\ \hline
    Max Generation & 20 & 20 \\ \hline
    Stagnation & Off & 10 \\ \hline
    Chromosome Length & 20 & 20 \\ \hline
    Target Fitness & 20 & 20 \\ \hline
    Crossover Rate & 100 & 100 \\ \hline
    Mutation Rate & 7 & 7 \\ \hline
    Tournament Rate & 100 & 50 \\ \hline
    Tournament Sample & 3 & 4 \\ \hline
    Open Reproduction Rate & NA & 5 \\ \hline
    Closed Reproduction Rate & NA & 45 \\ \hline
    Max Age & NA & 80 \\ \hline
    Base Approval & NA & 80 \\ \hline
    Goal Approval & NA & 100 \\ \hline
    \end{tabular}
    \end{table}
